Data-Driven Hardware-in-the-Loop Plant Modeling for Self-Driving Vehicles

### 2022-11-07 paperIEEE-ROSE2022-Pres.tex
Made changes to IEEE Presentation
I changed the graphs for the steering transfer function models and added some text to different slides.

\begin{frame}{Modeling Vehicle Subsystems}{System Requirements}
	\begin{block}{Specifications}
	\begin{minipage}[t]{0.62\linewidth}    
    Proposed vehicle subsystem models are expected to fulfill requirements listed below:
	\begin{itemize}
    		\item Resulting plant model will consist of reasonably accurate subsystem models
    		\item Subsystems can be used to create a HIL testbench
    		\item Steering model can handle very small changes in steering angles
    \begin{itemize}
		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
    \end{itemize}
	\end{itemize}
	\end{minipage}
	\begin{minipage}[t]{0.34\linewidth}
	\begin{figure}[h]
		\centering
    		\captionsetup{justification=centering, margin=0.5cm}
    		\includegraphics[width=1.5in]{figs/inkscape/nonlinearBehavior}
    		\caption{Steering Non-linear Behavior}
    		\label{fig:nonlinGraph}
	\end{figure}
	\end{minipage}
\end{block}
\end{frame}
%-------------------------

@@

\begin{frame}{Transfer Function Modeling}{Steering System Simulation}
	\begin{block}{Manual Mode}
 		\begin{figure}
		    \centering
		    \includegraphics[width=0.4\textwidth]{figs/img/byWireSteeringTransferFunctionModel}
		    \caption{Output of Estimated Manual System Model}
		        \label{fig:manualSteerModel}
 		\end{figure}
  	\end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Steering System Simulation (Cont.)}
	\begin{block}{By-Wire Mode}
		\begin{figure}
    			\centering
    			\includegraphics[width=0.4\textwidth]{figs/img/manualSteeringTransferFunctionModel}
    			\caption{Output of Estimated By-Wire System Model}
        		\label{fig:byWireSteerModel}
 		\end{figure}
	\end{block}
\end{frame}

%-------------------------
\begin{frame}{Transfer Function Modeling}{Acceleration System Simulation}
	\begin{block}{Manual Mode}
 		\begin{figure}
	    		\centering
	    		\includegraphics[width=0.4\textwidth]{figs/img/manualAccelTransferFunctionModel}
	        \caption{Output of Estimated Manual System Model}
	        \label{fig:manualAccelModel}
		\end{figure}
  	\end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Acceleration System Simulation (Cont.)}
	\begin{block}{By-Wire Mode}
		\begin{figure}
    			\centering
    			\includegraphics[width=0.4\textwidth]{figs/img/byWireAccelArxModel}
    			\caption{Output of Estimated By-Wire System Model}
        		\label{fig:byWireSteerModel}
 		\end{figure}
	\end{block}
\end{frame}

@@

%-------------------------
\begin{frame}{Neural Network Modeling}{Steering System Simulation}
	\begin{block}{}  		
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item Only a few samples are just outside of the accuracy requirements
			\item Transfer function model did not meet the accuracy requirements
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}
%-------------------------
\begin{frame}{Neural Network Modeling}{Acceleration System Simulation}
	\begin{block}{}
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item All samples within 2\% of the actual output
			\item Transfer function model did not have the same accuracy bounds
			\item Fewer concerns about connections in Simulink
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}
%-------------------------
\begin{frame}{Neural Network Modeling}{Brake System Simulation}
	\begin{block}{}
\begin{figure}[H]
  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/brakeSimulinkBlock}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item With this model, the error is kept below 5\%
			\item Able to easily track model performance
			\item Provides better results than the transfer function model
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
  		\end{figure}

>>>>

\begin{frame}{Modeling Vehicle Subsystems}{System Requirements}
	\begin{block}{Specifications}
	\begin{minipage}[t]{0.62\linewidth}    
    Proposed vehicle subsystem models are expected to fulfill requirements listed below'
    :
	\begin{itemize}
    		\item Resulting plant model will consist of reasonably accurate subsystem models
    		\item Subsystem models must reach an accuracy level of at least 95\% 
    		%\item Subsystems can be used to create a HIL testbench
    		\item Steering model can handle very small changes in steering angles
    \begin{itemize}
		\item smooth out any non-linear discontinuities that would normally be measured by the steering motor, especially for small changes in the steering angle, depicted in \autoref{fig:nonlinGraph}.
    \end{itemize}
	\end{itemize}
	\end{minipage}
	\begin{minipage}[t]{0.34\linewidth}
	\begin{figure}[h]
		\centering
    		\captionsetup{justification=centering, margin=0.5cm}
    		\includegraphics[width=1.5in]{figs/inkscape/nonlinearBehavior}
    		\caption{Steering Non-linear Behavior}
    		\label{fig:nonlinGraph}
	\end{figure}
	\end{minipage}
\end{block}
\end{frame}
%-------------------------

@@

\begin{frame}{Transfer Function Modeling}{Steering System Simulation}
	\begin{block}{Manual Mode}
	\begin{itemize}
			\item x-axis represents time in seconds 
			\item y-axis represents the steering angle in radians
			\item Model was able to achieve a best fit percentage of 83.25\% 
 		\end{itemize}
 		\begin{figure}
    			\centering
    			\includegraphics[width=0.4\textwidth]{figs/img/manualSteeringTransferFunctionModel}
    			\caption{Output of Estimated By-Wire System Model}
        		\label{fig:byWireSteerModel}
 		\end{figure}
% 		\begin{figure}
%		    \centering
%		    \includegraphics[width=0.4\textwidth]{figs/img/byWireSteeringTransferFunctionModel}
%		    \caption{Output of Estimated Manual System Model}
%		        \label{fig:manualSteerModel}
% 		\end{figure}
  	\end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Steering System Simulation (Cont.)}
	\begin{block}{By-Wire Mode}
		\begin{itemize}
			\item x-axis represents time in seconds 
			\item y-axis represents the steering angle in radians
			\item Model was able to achieve a best fit percentage of 86.87\% 
 		\end{itemize}
 		\begin{figure}
		    \centering
		    \includegraphics[width=0.4\textwidth]{figs/img/byWireSteeringTransferFunctionModel}
		    \caption{Output of Estimated Manual System Model}
		        \label{fig:manualSteerModel}
 		\end{figure}
%		\begin{figure}
%    			\centering
%    			\includegraphics[width=0.4\textwidth]{figs/img/manualSteeringTransferFunctionModel}
%    			\caption{Output of Estimated By-Wire System Model}
%        		\label{fig:byWireSteerModel}
% 		\end{figure}
	\end{block}
\end{frame}

%-------------------------
\begin{frame}{Transfer Function Modeling}{Acceleration System Simulation}
	\begin{block}{Manual Mode}
		\begin{itemize}
			\item x-axis represents time in seconds 
			\item y-axis represents the acceleration pedal position as a percentage 
			\item Model was able to achieve a best fit percentage of 98.3\% 
 		\end{itemize}
 		\begin{figure}
	    		\centering
	    		\includegraphics[width=0.4\textwidth]{figs/img/manualAccelTransferFunctionModel}
	        \caption{Output of Estimated Manual System Model}
	        \label{fig:manualAccelModel}
		\end{figure}
  	\end{block}
\end{frame}

\begin{frame}{Transfer Function Modeling}{Acceleration System Simulation (Cont.)}
	\begin{block}{By-Wire Mode}
			\begin{itemize}
			\item x-axis represents time in seconds 
			\item y-axis represents the acceleration pedal position as a percentage 
			\item Model was able to achieve a best fit percentage of 97.69\% 
 		\end{itemize}
		\begin{figure}
    			\centering
    			\includegraphics[width=0.4\textwidth]{figs/img/byWireAccelArxModel}
    			\caption{Output of Estimated By-Wire System Model}
        		\label{fig:byWireSteerModel}
 		\end{figure}
	\end{block}
\end{frame}

@@

%-------------------------
\begin{frame}{Neural Network Modeling}{Steering System Simulation}
	\begin{block}{}  		
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item \begin{small} Only a few samples are just outside of the accuracy requirements \end{small}
			%\item \begin{small} Transfer function model did not meet the accuracy requirements \end{small} 
			\item \begin{small} y-axis of top graph represents the actual and desired steering angle in radians \end{small} 
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/steeringNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}
%-------------------------
\begin{frame}{Neural Network Modeling}{Acceleration System Simulation}
	\begin{block}{}
  		\begin{figure}[H]
  			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelerationSimulinkBlock.jpg}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item \begin{small} All samples within 2\% of the actual output \end{small}
			\item \begin{small} y-axis of top graph represents the actual and desired acceleration pedal position as a percentage \end{small} 
			\item \begin{small} Fewer concerns about connections in Simulink \end{small} 
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/accelNeuralNetworkTrainedOutput2.jpg}
  		\end{figure}
	\end{block}
\end{frame}
%-------------------------
\begin{frame}{Neural Network Modeling}{Brake System Simulation}
	\begin{block}{}
\begin{figure}[H]
  			\centering \includegraphics[width=.48\linewidth , height=.37\textheight]{figs/img/brakeSimulinkBlock}\quad%
			\centering \begin{minipage}[b][0.4\textheight][c]{.45\linewidth}  \begin{itemize}
			\item \begin{small} With this model, the error is kept below 5\% \end{small} 
			\item \begin{small} y-axis of top graph represents the actual and desired brake pedal position as a percentage \end{small}
			\item \begin{small} Provides better results than the transfer function model \end{small} 
			\end{itemize} \end{minipage}\\[1em]
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFig.jpg}\quad%
			\centering \includegraphics[width=.45\linewidth , height=.37\textheight]{figs/img/brake_new_neuralNetworkFigLog2Test.jpg}
  		\end{figure}
